On this page
Introduction
Plot Output
Interactivity
Tables
LaTeX Math
Quarto HTML Basics
Norah Jones

March 22nd, 2021

Introduction
This a Quarto document. To learn more about Quarto see https://quarto.org.

Click the Code button in the header to see the full source code of this document.

Here we call the R summary() function—the function’s output is included immediately below:

summary(cars)

     speed           dist       
 Min.   : 4.0   Min.   :  2.00  
 1st Qu.:12.0   1st Qu.: 26.00  
 Median :15.0   Median : 36.00  
 Mean   :15.4   Mean   : 42.98  
 3rd Qu.:19.0   3rd Qu.: 56.00  
 Max.   :25.0   Max.   :120.00  
Plot Output
You can also embed plots, for example:

Code


Figure 1: Pressure
Note that the code-fold: true parameter was added to the code chunk to hide the code by default (click “Code” above the plot to see the code).

The use of the label and fig-cap options make this a cross-referenceable figure (see fig. 1).

Interactivity
You can also add interactive plots. For example:

library(dygraphs)
dygraph(nhtemp) %>% 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))


48
49
50
51
52
53
54
55
1920
1930
1940
1950
Figure 2: New Haven Temperatures
Tables
Use the knitr::kable() function to print tables as HTML:

knitr::kable(head(ggplot2::diamonds))

carat	cut	color	clarity	depth	table	price	x	y	z
0.23	Ideal	E	SI2	61.5	55	326	3.95	3.98	2.43
0.21	Premium	E	SI1	59.8	61	326	3.89	3.84	2.31
0.23	Good	E	VS1	56.9	65	327	4.05	4.07	2.31
0.29	Premium	I	VS2	62.4	58	334	4.20	4.23	2.63
0.31	Good	J	SI2	63.3	58	335	4.34	4.35	2.75
0.24	Very Good	J	VVS2	62.8	57	336	3.94	3.96	2.48
LaTeX Math
You can also include LaTeX math:

P
(
A
=
2
|
A
2
B
>
4
)
P(A=2 
∣
∣
​
  
B
A 
2
 
​
 >4)

Source Code

---
title: "Quarto HTML Basics"
author: "Norah Jones"
date: "March 22nd, 2021"
toc: true
format:
  html:
    html-math-method: katex
    code-tools: true
    self-contained: true
execute:
  warning: false
---

## Introduction

This a Quarto document. To learn more about Quarto see <https://quarto.org>.

Click the **Code** button in the header to see the full source code of this document.

Here we call the R `summary()` function---the function's output is included immediately below:

```{r}
summary(cars)
```

## Plot Output

You can also embed plots, for example:

```{r}
#| label: fig-pressure
#| fig-cap: "Pressure"
#| code-fold: true

library(ggplot2)
dat <- data.frame(cond = rep(c("A", "B"), each=10),
                  xvar = 1:20 + rnorm(20,sd=3),
                  yvar = 1:20 + rnorm(20,sd=3))

ggplot(dat, aes(x=xvar, y=yvar)) +
    geom_point(shape=1) + 
    geom_smooth() 
```

Note that the `code-fold: true` parameter was added to the code chunk to hide the code by default (click "Code" above the plot to see the code).

The use of the `label` and `fig-cap` options make this a cross-referenceable figure (see @fig-pressure).

## Interactivity

You can also add interactive plots. For example:

```{r}
#| label: fig-temperatures
#| fig-cap: "New Haven Temperatures"

library(dygraphs)
dygraph(nhtemp) %>% 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))
```

## Tables

Use the `knitr::kable()` function to print tables as HTML:

```{r}
knitr::kable(head(ggplot2::diamonds))
```


## LaTeX Math

You can also include LaTeX math:

$$
P\left(A=2\middle|\frac{A^2}{B}>4\right)
$$

